---
title: "STAT 331 Portfolio"
author: "Your Name Goes Here"
format: 
  html: 
    self-contained: true
layout: margin-left
editor: visual
execute: 
  eval: false
  echo: true
---

[**My Grade:**]{.underline} I believe my grade equivalent to course work evidenced below to be an \_\_.

[**Learning Objective Evidence:**]{.underline} In the code chunks below, provide code from a Lab or Challenge assignment where you believe you have demonstrated proficiency with the specified learning target. Be sure to specify **where** the code came from (e.g., Lab 4 Question 2). 

## Working with Data

**WD-1: I can import data from a _variety_ of formats (e.g., csv, xlsx, txt, etc.).**

- `csv`
```{r wd-1-csv}

```

- `xlsx`
```{r wd-1-xlsx}

```

- `txt`
```{r wd-1-txt}

```

**WD-2: I can select necessary columns from a dataset.**

```{r wd-2}

```

**WD-3: I can filter rows from a dataframe for a _variety_ of data types (e.g., numeric, integer, character, factor, date).**

- numeric
```{r wd-3-numeric}

```


- character -- specifically a string (example must use functions from **stringr**)
```{r wd-3-string}

```

- factor
```{r wd-3-factor}

```

- date (example must use functions from **lubridate**)
```{r wd-3-date}

```

**WD-4: I can modify existing variables and create new variables in a dataframe for a _variety_ of data types (e.g., numeric, integer, character, factor, date).**

- numeric (using `as.numeric()` is not sufficient)
```{r wd-4-numeric}

```


- character -- specifically a string
```{r wd-4-string}

```


- factor (example must use functions from **forcats**)
```{r wd-4-factor}

```

- date (example must use functions from **lubridate**)
```{r wd-4-date}

```

**WD-5: I can use mutating joins to combine multiple dataframes.**

- `left_join()`
```{r wd-5-left}

```

- `right_join()`
```{r wd-5-right}

```

- `inner_join()`
```{r wd-5-inner}

```

- `full_join()`
```{r wd-5-full}

```

**WD-6: I can use filtering joins to filter rows from a dataframe.**

- `semi_join()`
```{r wd-6-semi}

```

- `anti_join()`
```{r wd-6-anti}

```

**WD-7: I can pivot dataframes from long to wide and visa versa**

- `pivot_longer()`
```{r wd-7-long}

```

- `pivot_wider()`
```{r wd-7-wide}

```

## Reproducibility

**R-1: I can create professional looking, reproducible analyses using RStudio projects, Quarto documents, and the here package.**

I've done this in the following provided assignments:


**R-2: I can write well documented and tidy code.**

- Example of **ggplot2** plotting
```{r r-2-1}

```

- Example of **dplyr** pipeline
```{r r-2-2}

```

- Example of function formatting
```{r r-2-3}

```


**R-3: I can write robust programs that are resistant to changes in inputs.**

- Example -- any context
```{r r-3-1}

```

- Example of function stops
```{r r-3-2}

```

## Data Visualization & Summarization

**DVS-1: I can create visualizations for a _variety_ of variable types (e.g., numeric, character, factor, date)**

- at least two numeric variables
```{r dvs-1-num}

```


- at least one numeric variable and one categorical variable
```{r dvs-2-num-cat}

```


- at least two categorical variables
```{r dvs-2-cat}

```

- dates (timeseries plot)
```{r dvs-2-date}

```

**DVS-2: I use plot modifications to make my visualization clear to the reader.**

- I can ensure people don't tilt their head
```{r dvs-2-1}

```

- I can modify the text in my plot to be more readable
```{r dvs-2-2}

```

- I can reorder my legend to align with the colors in my plot
```{r dvs-2-3}

```

**DVS-3: I show creativity in my visualizations**

- I can use non-standard colors
```{r dvs-3-1}

```

- I can use annotations
```{r dvs-3-2}

```

- I can ...
```{r dvs-3-3}

```

**DVS-4: I can calculate numerical summaries of variables.**

- Example using `summarize()`
```{r dvs-4-1}

```

- Example using `across()`
```{r dvs-4-2}

```

**DVS-5: I can find summaries of variables across multiple groups.** 

- Example 1
```{r dvs-5-1}

```

- Example 2
```{r dvs-5-2}

```

**DVS-6: I can create tables which make my summaries clear to the reader.**

- Example with `kable()`
```{r dvs-6-1}

```

- Example with `gt()`
```{r dvs-6-2}

```

**DVS-7: I show creativity in my tables.**

- Example with `kable()`
```{r dvs-7-1}

```

- Example with `gt()`
```{r dvs-7-2}

```

## Program Efficiency

**PE-1: I can write concise code which does not repeat itself.**

- using a single function call with multiple inputs (rather than multiple function calls)
```{r pe-1-one-call}

```

- `across()`
```{r pe-1-across}

```

- `map()` functions
```{r pe-1-map-1}

```

**PE-2: I can write functions to reduce repetition in my code.**

- Function that operates on vectors
```{r pe2-1}

```

- Function that operates on data frames
```{r pe2-2}

```

**PE-3:I can use iteration to reduce repetition in my code.**

- `across()`
```{r pe-3-across}

```

- `map()` function with **one** input (e.g., `map()`, `map_chr()`, `map_dbl()`, etc.)
```{r pe-3-map-1}

```

- `map()` function with **more than one** input (e.g., `map_2()` or `pmap()`)
```{r pe-3-map-2}

```

**PE-4: I can use modern tools when carrying out my analysis.**

- I can use functions which are not superseeded or deprocated
```{r pe-4-1}

```

- I can connect a data wrangling pipeline into a `ggplot()`
```{r pe-4-2}

```

## Data Simulation & Modeling

**DSM-1: I can simulate data from a _variety_ of probability models.**

- Example 1
```{r dsm-1-1}

```

- Example 2
```{r dsm-1-2}

```

**DSM-2: I can fit a linear regression and extract necessary summary measures.**

- I can fit a linear regression
```{r dsm-2-1}

```

- I can extract necessary summary measures from a linear regression model
```{r dsm-2-2}

```


## Revising My Thinking
<!-- How did you revise your thinking throughout the course? How did you revise your thinking on the code examples you have provided in your portfolio? -->



## Extending My Thinking
<!-- How did you extended your thinking throughout the course? How did you extend your thinking on the code examples you have provided in your portfolio? -->



## Peer Support & Collaboration
<!-- Include an image of feedback you gave that you are proud of (either in a peer review or in Discord) -->