---
title: "STAT 331 Portfolio"
author: "Your Name Goes Here"
format: 
  html: 
    self-contained: true
layout: margin-left
editor: visual
execute: 
  eval: false
  echo: true
---

[**My Grade:**]{.underline} I believe my grade equivalent to course work evidenced below to be an \_\_.

[**Learning Objective Evidence:**]{.underline} In the code chunks below, provide code from a Lab or Challenge assignment where you believe you have demonstrated proficiency with the specified learning target. Be sure to specify **where** the code came from (e.g., Lab 4 Question 2). 

## Working with Data

**WD-1: I can import data from a _variety_ of formats (e.g., csv, xlsx, txt, etc.).**

- `csv`
```{r wd-1-csv}

```

- `xlsx`
```{r wd-1-xlsx}

```

- `txt`
```{r wd-1-txt}

```

**WD-2: I can select necessary columns from a dataset.**

```{r wd-2}

```

**WD-3: I can filter rows from a dataframe for a _variety_ of data types (e.g., numeric, integer, character, factor, date).**

- numeric
```{r wd-3-numeric}

```


- character -- specifically a string
```{r wd-3-string}

```


- factor
```{r wd-3-factor}

```

- date
```{r wd-3-date}

```

**WD-4: I can modify existing variables and create new variables in a dataframe for a _variety_ of data types (e.g., numeric, integer, character, factor, date).**

- numeric
```{r wd-4-numeric}

```


- character -- specifically a string
```{r wd-4-string}

```


- factor
```{r wd-4-factor}

```

- date
```{r wd-4-date}

```

**WD-5: I can use mutating joins to combine multiple dataframes.**

- `left_join()`
```{r wd-5-left}

```

- `right_join()`
```{r wd-5-right}

```

- `inner_join()`
```{r wd-5-inner}

```

- `full_join()`
```{r wd-5-full}

```

**WD-6: I can use filtering joins to filter rows from a dataframe.**

- `semi_join()`
```{r wd-6-semi}

```

- `anti_join()`
```{r wd-6-anti}

```

**WD-7: I can pivot dataframes from long to wide and visa versa**

- `pivot_longer()`
```{r wd-7-long}

```

- `pivot_wider()`
```{r wd-7-wide}

```

## Reproducibility

**R-1: I can create professional looking, reproducible analyses using RStudio projects, Quarto documents, and the here package.**

I've done this in the following provided assignments:


**R-2: I can write well documented and tidy code.**

- Example 1
```{r r-2-1}

```

- Example 2
```{r r-2-2}

```

**R-3: I can write robust programs that are resistant to changes in inputs.**

- Example 1
```{r r-3-1}

```

- Example 2
```{r r-3-2}

```

## Data Visualization & Summarization

**DVS-1: I can create visualizations for a _variety_ of variable types (e.g., numeric, character, factor, date)**

- numeric variables
```{r dvs-1-num}

```


- numeric variables and categorical variables
```{r dvs-2-num-cat}

```


- categorical variables
```{r dvs-2-cat}

```

- dates
```{r dvs-2-date}

```

**DVS-2: I use plot modifications to make my visualization clear to the reader.**

- Example 1
```{r dvs-2-1}

```

- Example 2
```{r dvs-2-2}

```

**DVS-3: I show creativity in my visualizations**

- Example 1
```{r dvs-3-1}

```

- Example 2
```{r dvs-3-2}

```

**DVS-4: I can calculate numerical summaries of variables.**

- Example 1
```{r dvs-4-1}

```

- Example 2
```{r dvs-4-2}

```

**DVS-5: I can find summaries of variables across multiple groups.** 

- Example 1
```{r dvs-5-1}

```

- Example 2
```{r dvs-5-2}

```

**DVS-6: I can create tables which make my summaries clear to the reader.**

- Example 1
```{r dvs-6-1}

```

- Example 2
```{r dvs-6-2}

```

**DVS-7: I show creativity in my tables.**

- Example 1
```{r dvs-7-1}

```

- Example 2
```{r dvs-7-2}

```

## Program Efficiency

**PE-1: I can write concise code which does not repeat itself.**

- using a single function call
```{r pe-1-one-call}

```

- `across()`
```{r pe-1-across}

```

- `map()` functions
```{r pe-1-map-1}

```

**PE-2: I can write functions to reduce repetition in my code.**

- Example 1
```{r pe2-1}

```

- Example 2
```{r pe2-2}

```

**PE-3:I can use iteration to reduce repetition in my code.**

- `across()`
```{r pe-3-across}

```

- `map()` functions (Provide 2 Examples)
```{r pe-3-map-1}

```

```{r pe-3-map-2}

```

**PE-4: I can use modern tools when carrying out my analysis.**

- Example 1
```{r pe-4-1}

```

- Example 2
```{r pe-4-2}

```

## Data Simulation & Modeling

**DSM-1: I can simulate data from a _variety_ of probability models.**

- Example 1
```{r dsm-1-1}

```

- Example 2
```{r dsm-1-2}

```

**DSM-2: I can fit a linear regression and extract necessary summary measures.**

- Example 1
```{r dsm-2-1}

```

- Example 2
```{r dsm-2-2}

```


## Revising My Thinking
<!-- How did you revise your thinking throughout the course? How did you revise your thinking on the code examples you have provided in your portfolio? -->



## Extending My Thinking
<!-- How did you extended your thinking throughout the course? How did you extend your thinking on the code examples you have provided in your portfolio? -->



## Peer Support & Collaboration
<!-- Include an image of feedback you gave that you are proud of (either in a peer review or in Discord) -->