---
title: "Challenge 3"
author: "Jake McDonald"
format: 
  html:
    self-contained: true
editor: visual
---

#1

```{r setup}
#| output: false
library(tidyverse)
library(here)
hiphop <- read_csv(here::here("supporting_artifacts", "learning_targets", "hiphop.csv"))
```

#2

```{r data wrangling}

hiphop2 <- hiphop |> 
  mutate(ethnic_cat = if_else(ethnic == "white", "white", "non-white")) |> 
  select(c(subj, sex, intl:hiphop, ethnic_cat))
```

#3

```{r male vs female}

hiphop2 |> 
  group_by(sex) |> 
  summarize(across(intl:hiphop, mean, na.rm = TRUE)) |> 
  summarize(across(intl:hiphop, diff, na.rm = TRUE))
```

The largest difference in the average number of artists participants reported liking for males versus females was the rock genre.

#4

```{r white vs. non-white}

hiphop2 |> 
  group_by(ethnic_cat) |> 
  summarize(across(intl:hiphop, mean, na.rm = TRUE)) |> 
  summarize(across(intl:hiphop, diff, na.rm = TRUE))
```

The largest difference in the average number of artists participants reported liking in each genre was for whites vs. non-whites was also the international music genre.

Study Design Critique

1.  The sample is has a much larger proportion of white people than people of color, which would not give an accurate representation of the greater population.

2.  Additionally, I believe that some of the pop-culture/AAE language references could be deemed offensive, as they display generalizations on how African Americans speak
