---
title: "Lab 9"
author: "Jake McDonald"
format: 
  html:
    self-contained: true
editor: visual
---

## Lab 9

```{r library & data}
#| echo: False
#| output: False
library(tidyverse)
library(broom)
library(here)
library(knitr)

a_names <- read_csv(here::here("supporting_artifacts", "learning_targets", "StateNames_A.csv"))
```

```{r rename}
#| output: false
#renaming the sex column
a_names <-a_names |> 
  rename("Sex" = Gender)
```

## 3 Summarizing & Visualizing the Number of Allisons

#1/2

```{r summarizing number of Allisons}
summary_names <- a_names |> 
  filter(Name == "Allison") |> 
  pivot_wider(names_from = Sex, values_from = Count) |>
  group_by(State) |> 
  #get sum by state
  summarize(across(.cols = c("F", "M"), .fns = sum)) |> 
  mutate(across(.cols = c("F", "M"), ~replace_na(., 0))) |> 
  rename("Number of Females Named Allison" = F, 
         "Number of Males Named Allison" = M)

summary_names
```

#3

```{r Allison Data Wrangling}
#| output: false
vis_names <- a_names |>
  filter(Name == "Alison",
         Sex == "F") |> 
  pivot_wider(names_from = Sex, values_from = Count) |> 
  group_by(Year) |>
  summarize(sum = sum(F), .groups = "keep")
```

```{r visulization of Allisons}
model_names <- vis_names |> 
  ggplot(mapping = aes(
    x = Year,
    y = sum)) +
  geom_point()+
  geom_line()+
  labs(
    y = "",
    x = "Years",
    title = "Number of People Named Allison Over Time")

model_names
```

## 4 Modeling the Number of Allisons

#4

```{r model fit}
lm_names <- vis_names |> 
  lm(sum ~ Year, data = _)

lm_names
```

#5

```{r regression visualization}
visual_lm <- vis_names |> 
  ggplot(mapping = aes(
    x = Year, 
    y = sum)) +
  geom_point() +
  #plotting residual line:
  stat_smooth(method = "lm") +
  labs(x = "Year",
       y = "",
       title = "Regression Model Visulization for \nSum of People Named Allison and Year")

visual_lm
```

#6 Regression Equation:

## Number of Allisons = 59619.99 - 29.07(Year)

#7 Plot the Residuals

```{r residual plot}

resid <- lm_names |> 
  #getting the residuals:
  broom::augment() |> 
  #plotting
  ggplot(mapping = aes(y = .resid, x = .fitted)) +
  geom_point() +
  labs(
    x = "Number of Allisons",
    y = "",
    title = "Plotted Residuals of LRM \nUsing Year to Predict Number of Allison"
  )

resid
```

When the number of Allisons are between 1250 and 1400, the Year variable predicts the, to be lower than in actuality. Overall, however, because there a not very much of a pattern, we can reasonably conclude that the data is unbiased, not heteroskedastic, and of equal variance.

#8

Because the beta on the year variable is negative, there is evidence to believe that the popularity of the name Allison is declining over the years.

## 5 Spelling by State

#1 Visualization of the name 'Allan'

```{r Allan Wrangling}
#| output: false
allan <- a_names |> 
  filter(Name == "Allan" | Name == "Alan" | Name == "Allen") |> 
  group_by(Year, Name) |> 
  #sum of the different spellings
  summarize(total = sum(Count), .groups = "keep") |> 
  #creating new columns for the spellings
  pivot_wider(names_from = Name, values_from = total)
```

```{r Allan Spelling Visualization}
allan_vis <- allan |>
  ggplot(aes(x = Year)) +
  #getting each of the differnt lines and colors
  geom_line(aes(y = Allen, color = "Allen")) +
  geom_line(aes(y = Allan, color = "Allan")) +
  geom_line(aes(y = Alan, color = "Alan")) +
  scale_color_manual(name='Name Spelling',
                     breaks=c('Allen', 'Allan', 'Alan'),
                     values=c('Allen'='pink', 'Allan'='blue', 'Alan'='purple')) +
  labs(
    x = "Year",
    y = "Count",
    title = "Popularity of Allan Name Spellings Over Time") +
  #adding a theme to the plot
  theme(plot.title = element_text(hjust = 0.5))

allan_vis
```

#2

```{r Allan by State}
allan_state <- a_names |> 
  filter(Name == "Allan" | Name == "Alan" | Name == "Allen",
         Year == 2000,
         State == "CA" | State == "PA") |> 
  group_by(State, Name) |> 
  #get the sum by state for each name
  summarize(total = sum(Count), .groups = "keep") |> 
  pivot_wider(names_from = Name, values_from = total) |> 
  #replace na's
  mutate(across(.cols = "Alan":"Allen", ~replace_na(., 0)))

allan_state
```

#3 Converting to Proportions

```{r State Proportions}
proportions <- allan_state |> 
  pivot_longer(cols = "Alan":"Allen", names_to = "Name", values_to = "Count") |> 
  #pivot to include by columns for state
  pivot_wider(names_from = State, values_from = Count) |> 
  #Proportions conversion
  mutate(CA = CA/sum(CA)) |> 
  mutate(PA = PA/sum(PA)) |> 
  pivot_longer(cols = "CA":"PA", names_to = "State", values_to = "Proportion") |> 
  pivot_wider(names_from = Name, values_from = Proportion)

proportions
```
