---
title: "Data Import Practice"
author: "Jake McDonald"
format: 
  html:
    self-contained: true
editor: visual
---

```{r}
#| output: false
library(tidyverse)
library(readxl)
library(here)
```

## Step 1: Read in the dataset `ages.csv`.

```{r csv}
#| output: false
# Code to read in the ages.csv data goes here! 
read_csv(here("supporting_artifacts", "learning_targets", "Ages_Data", "ages.csv"))

```

## Step 2: Read in the dataset `ages_tab.txt`

```{r txt}
#| output: false
# Code to read in the ages_tab.txt data goes here! 
read_delim(here("supporting_artifacts", "learning_targets", "Ages_Data", "ages_tab.txt"), 
           delim = " ")

```

## Step 3: Read in the dataset `ages_mystery.txt`

```{r ages mystery txt}
# Code to read in the ages_mystery.txt data goes here! 
read_delim(here("supporting_artifacts", "learning_targets", "Ages_Data", "ages_mystery.txt"), 
           delim = "|")

```

## Step 4: Read in the dataset `ages.xlsx`

```{r}
# Code to read in the ages.xlsx data goes here! 
read_xlsx(here("supporting_artifacts", "learning_targets", "Ages_Data", "ages.xlsx"))
```

## Step 5: Both `read.csv` and `read.table` have an optional argument called `stringsAsFactors`. Figure out what this does.

The `stringsAsFactors` argument converts variables that are strings (or characters) into a `factor` data type. A `factor` data type is different from a character in how it stores the values of the variable.

## Step 6: Find a way to use `read_csv()` to read `ages.csv` with the variable "Name" as a factor and "Age" as a character.

```{r}
# Code to read in the ages.csv with "Name" as a factor and "Age" as a character goes here! 
read_csv(here("supporting_artifacts", "learning_targets", "Ages_Data", "ages.csv"), 
         col_types = list("f", "c"))
```

------------------------------------------------------------------------
